\section{Conclusion}

% State the problem
Since the rise of Big Tech and its business models, respecting customers' privacy becomes an important attribute.

% Sum up paper
After establishing the need to guarantee the preservation of customers' privacy, this paper discussed a plethora of \gls{PPM}s and their implications. 
These consist of five separate steps. 
Starting with data collection and generation, the basis of everything discussed so far. 
Next, we have looked at ways to store data, followed by available protections during the publishing phase. 
Data modification features a wide range of different methods. Finally, extracting information and knowledge from data is the most valuable for company strategies.

% Discuss implications
Furthermore, these methods are related to the most common \gls{DDBM}s. Data mining has proven to be a valuable asset in gaining knowledge as a competitive advantage. 

% Summarize last section
Unfortunately, this comes at the cost of risking the trust of users.

% Further research
Further research is needed to relate \gls{PPM}s and their impact on consumer trust in \gls{DDBM}s.
A valid approach could be measuring the impact of \gls{PbE} on trust.

% Limitations
This survey paper was written by three computer science engineering students of Ghent University for one of their master courses.
They do not conduct any research themselves.
The intent of this paper is for it to be their first exploration in academic research.
None of the authors claim to have expert knowledge on the discussed topics, 
and this survey was entirely based on research of others.
