\section{The role of data for big tech}

The current digital age offers many possibilities, which companies belonging to Big Tech, take great advantage of. 
Companies such as Alphabet (Google), Amazon and Apple define their place on the market by means of technological innovations.
Because of their influence on present markets, they cannot be removed from today's view of society.

\subsection{Big Tech's advantage}
\label{s:big tech}

One of the big advantages Big Tech companies have, lies in the knowledge gained from personal data, which can improve customer relationships.
Data analysts often use machine learning and artificial intelligence to perform the necessary investigations \cite{Creser2021}.
On the contrary, conventional markets can only estimate the customers' interests based on the current market price. 
This includes smaller businesses that do not reside on the internet and do not strongly depend on personal data.
This market price provides only so much information, and it is often not trivial to derive the correct information. 
On the opposite side, the Big Tech companies are ahead with this valuable data at their disposal. 
They can be more accurate and direct using the aforementioned techniques, which guide the customers in their choices.

With Big Tech companies having the advantage of already accumulated data, it is challenging for small companies to compete in the long run.
Newer products similar in functionality compared to the ones of Big Tech companies can easily be suppressed by these companies.
There have been proposals to level the playing field, e.g., initiating a progressive data-sharing mandate resulting in smaller companies having access to the same tools \cite{Viktor2018}.

We can conclude that Big Tech is as big as it is now as a consequence of the large boost in data collection and processing. 
The influence of these companies is noticeable in a variety of domains, from an economic standpoint, but also from a democratic one \cite{Fukuyama2021, Ghosh2021}.
